---
title: "01-run-experiment"
author: "Ryan Wesslen"
date: "April 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

## Run Bumper Sticker Experiment

First, get the two R packages: `tweetscores` and `twitteR`. You will need `devtools` to install `tweetscores`.

```{r eval=FALSE}
devtools::install_github("pablobarbera/twitter_ideology/pkg/tweetscores")
install.packages("twitterR")

library(tweetscores); library(twitteR)
```

### Use one day full sample

For our experiment, we used one full day 1% streaming data for Sept 28, 2017 -- 2.58MM unique users for 3,423,287 tweets

For an example of how to pull 1% streaming using streamR package, see [Social Media Workshop](https://github.com/wesslen/summer2017-socialmedia/blob/master/day1/twitter-streaming.Rmd).

The id file only needs to include the user profile (actor.id) of the users you want to ping.

```{r eval=FALSE}
# dataset not provided
id <- readr::read_csv("./data/userid20170928.csv")
id$ids <- as.character(id$ids)
```

Next, point to your credentials file (for info to set up, see README of <https://github.com/pablobarbera/twitter_ideology>)

```{r eval=FALSE}
credentials <- "~/TwitterSample/credentials/"
```

### Running the experiment

First, let's initialize our dataframe.

```{r eval=FALSE}
#initialize columns/formats
df <- getUsersBatch(ids=id$ids[1], # choose first one to initialize the dataset
              oauth_folder= credentials,
              include_entities = TRUE)

#initialize a timestamp to show when the pass completed
df$timestamp <- Sys.time()

# remove all entries to initialize (empty dataframe with correct column formatting)
df <- df[0,]
```

Next, set up the parameters for the experiment.

```{r eval=FALSE}
# set stop time for the experiment
stopTime <- "2017-10-14 00:00:00 EDT"

# file name to save results
fileName <- "./data/experiment.csv"

# while loop to rerun after each pass
while(Sys.time() < stopTime){
  userdata <- getUsersBatch(ids = id$ids,
                            oauth_folder = credentials,
                            include_entities = TRUE)
  userdata$timestamp <- Sys.time() # mark after the users batch completes
  df <- rbind(df, userdata)        # append the new pass with the previous passes
  write_csv(df, fileName) # save the file as a CSV
}
```


## Future Work

Moving forward, there are two ways to improve upon this code.

First, noSQL databases would be better way to store the data (e.g., MongoDB) than flat (json or CSV) files.

Second, `twitteR` package is deprecated. `rtweet` by Mike Kearney (see [link](http://rtweet.info/)) is a better long-term Twitter API package in R. A better solution would be to migrate to `rtweet`. The problem is the `tweetscores` packages uses `twitteR` so reconciliation would be needed before migrating to `rtweet`.